\documentclass[12pt,foldmark]{leaflet}
\usepackage{scoutsLeaflet}

\begin{document}
% Front cover page (1)
\scoutstitle{TECHNICAL VOLUNTEERING}
{Flexible opportunities to volunteer your IT, engineering and technical skills}

% Inner lhs page (2)
\withrotationtrue
\section{Volunteering Your Technical Skills to Help Scouting}
\withrotationfalse
\subsection{If you know anything about \ldots}
\vspace{1cm}
\begin{itemize}
    \item Creating a website
    \item Google Apps or Office 365
    \item Writing software applications
    \item Amateur radio
    \item Electronics
\end{itemize}
\vspace{1cm}
\subsection{We would love to hear from you!}
\newpage

% Inner middle page (3)
We have teams of adults, who wish to volunteer on a flexible basis, called `Active Support Units.' They allow people to fit their volunteering around their other commitments, to use their individual talents and to volunteer with friends.

Not everyone can contribute to a weekly commitment. Active Support Units allow people to make a valuable contribution to a movement that continues to develop and grow, providing activities and opportunities for many young people.

In the Mersey Weaver District, which covers Widnes, Runcorn, Frodsham, Helsby and the surrounding villages, we have a Technical Active Support Unit. It provides help and advice for the Scout Groups in our District on matters involving all kinds of technology.

Membership of the Unit is open to anyone over the age of 18. If you would like to use your technical skills for the good of your local community and young people, this is your opportunity. Please get in touch.
\vfill
\subsubsection{Thank you for your interest}
\newpage

% Inner rhs page (4)
\withrotationtrue
\section{WHY SCOUTING?}
\withrotationfalse
The Scout Association is the UK's largest mixed youth movement. We offer activities, adventure and personal development opportunities to more than 400 000 young people and 100 000 adult volunteers.

We believe in helping young people grown in confidence and explore their potential as well as providing a range of adult volunteering opportunities.
\vfill
\epigraph{\textit{``Flexible volunteering means I can fit Scouting around my family and other commitments. You can do it too!''}}{Bear Grylls, Chief Scout}

\newpage

% Folded in page (5)
\input{merseyWeaverContactPage}

% Back cover page (6)
\input{leafletPage6}

\end{document}